---
title: "Using the HDIAnalysis Package"
author: "Bhagavath Kumar Krishnan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HDIAnalysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The `HDIAnalyze` package provides tools to read, print, summarize and visualize the Human Development Indicators (HDI) data. The analysis of T]two countries are considered which are Ireland and India.

## Loading Necessary Libraries

Loading all the libraries in the beginning to make sure that all the dependencies are available.

```{r setup, include=FALSE, warning=FALSE}
library(data.table)
library(ggplot2)
library(dplyr)
library(knitr)
```

## Loading the Package

```{r load_library, warning=FALSE}
library(HDIAnalyze)
```

# Ireland

The usage of `HDIAnalyze` package (and its methods) for the country Ireland is discussed below.

## Reading and Printing HDI Data

Below is the demonstration of how to use `read_hdi` function to read a HDI data and to perform basic operation.
We have two methods of printing the output:

+ `print1.HDIAnalyze`: Prints the first 5 observations of the HDI data with corresponding columns and their values.
+ `print2.HDIAnalyze`: Prints the first 5 observations of the HDI data in a tabular format.

```{r load_print_data, warning=FALSE}
# Load the data
hdi_irl <- read_hdi("hdro_indicators_irl.csv")
```

```{r}
# Print the data (method 1)
print1.HDIAnalyze(hdi_irl)
```

```{r}
# Print the data(method 2)
print2.HDIAnalyze(hdi_irl)
```

## Other methods of `HDIAnalyze` Class

`HDIAnalyze` class supports several other methods for data analysis and visualization. It provides a summary statistics corresponding to each indicator values and a box plot corresponding to each indicators whose values are less than 100.

``` {r summary_data}
summaryHDI.HDIAnalyze(hdi_irl)
```

```{r plot_method, fig.height=5, fig.width=7, fig.align='center'}
plotHDI.HDIAnalyze(hdi_irl)
```

# India

The above methods of `HDIAnalysis` are discussed for a second country of India.

## Read data and Print methods

```{r read_ind}
hdi_ind <- read_hdi("hdro_indicators_ind.csv")

print1.HDIAnalyze(hdi_ind)
```

```{r}
print2.HDIAnalyze(hdi_ind)
```

## Summary Statistics

```{r}
summaryHDI.HDIAnalyze(hdi_ind)
```

## Plot

```{r fig.height=5, fig.width=7, fig.align='center'}
plotHDI.HDIAnalyze(hdi_ind)
```
